\chapter{Conclusion}

\section{Summary of Project}

In this Final-Year Project, we have proposed an integrated
processing system for transcription and captioning of multimedia
data. The system architecture has been designed, and the major
functionalities implemenented; the system fulfills the primary
objectives of realising the following processing tasks:

\begin{itemize}
    \item Transcription of individual audio and video files using different
    transcription solutions
    \item Transcription of multi-channel audio recording
    \item Keyframe captioning of video files
    \item Visualization of the generated transcripts and captions
\end{itemize}

Furthermore, the system is able to fulfill five major quality attributes:

\begin{itemize}
    \item Modularity --- system components are independent in operation, and
    self-contained
    \item Extensibility --- system components are easily modified and upgraded
    to suit different processing requirements
    \item Robustness --- aggressive error detection, completion checking and
    process resumption capabilities for every component
    \item Versioning --- built-in mechanism for modular and output versioning
    \item Logging and Reporting --- helpful diagnostic messages at both system
    and component level
\end{itemize}

Overall, the implemenented system achieves its desired goals.

\section{Future Recommendations}

As described in Section~\ref{sec:in:sco}, the scope of this project starts only at
the processing steps and stops after visualization, and there is no GUI implemenented
at the moment. Hence, two recommendations would be briefly outlined.

\subsubsection{Development of a GUI}

The current implementation uses a CLI, which is not friendly to the users. A GUI
could be developed on top of the current system; the system would then acts as a
backend.

This would open up the usage of the system to common users.

\subsubsection{Development of a functioning indexing system}

The most important part of a multimedia processing pipeline after processing is 
the indexing and storage of data. Such a system if implemenented could have major
benefits, allowing researchers and users to better utilise the data processed by
our system.
